---
title: "Project data cleaning"
author: "Xueyan Hu"
date: "2023-02-22"
output: html_document
---


# Processing script with code pulled in

This is essentially the same as the other Quarto file, but now the code is not inside this file. Instead, it is pulled in from the R script using the code chunk labels.




# Setup

This needs to run to load the R script so we can include the code chunks below.

Note that you can pull in more than one R script if you want.

```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('processingcode.R')
```




Load needed packages. Instead of having R commands here, this just pulls in the code from the R script we loaded above and labelled.


```{r, packages, message = FALSE, warning = FALSE}
```



# Data loading

Note that for functions that come from specific packages (instead of base R), I often specify both package and function like so:
package::function() that's not required one could just call the function specifying the package makes it clearer where the function "lives",
but it adds typing. You can do it either way.

```{r, loaddata}
```


# Explore data

Several ways of looking at the data

```{r, exploredata}
```


# Cleaning

The data looks generally clear before cleaning. So I just want to make sure that "Day" could be defined as a categorical variable but not a numeric variable.

```{r, cleandata1}
```


# Save data 

All done, data is clean now. Time to save.
Let's assign at the end to some final variable, this makes it easier to add further cleaning steps above.

Finally, we save the clean data as RDS file. I suggest you save your processed and cleaned data as RDS or RDA/Rdata files. 
This preserves coding like factors, characters, numeric, etc.  If you save as CSV, that information would get lost.
However, CSV is better for sharing with others since it's plain text. If you do CSV, you might want to write down somewhere what each variable is.

See here for some suggestions on how to store your processed data:
http://www.sthda.com/english/wiki/saving-data-into-r-data-format-rds-and-rdata

```{r, savedata}
```



